Setting up Data

### 2020-02-07 src/SetupData.Rmd
can't remeber changes

#AP_mouse_table_w.Ages
#use the above table to pull the male mouse levels

male_mouse.av <-  AP_mouse_table_w.Ages %>% filter(sex== "male")

#formate the table for pluggin into models

>>>>

#AP_mouse_table_w.Ages
#use the above table to pull the male mouse levels
male_mouse.av <-  AP_mouse_table_w.Ages %>% filter(sex== "male")

#add the Rec.group markers

#mouse.avs_4MM$Rec.group <- ifelse(grepl("PWD", mouse.avs_4MM$strain), 1, 
#                            ifelse(grepl("MSM", mouse.avs_4MM$strain), 1,
#                             ifelse(grepl("SKIVE", mouse.avs_4MM$strain), 1, 0)) )

#formate the table for pluggin into models
```
